---
title: "testing_main_figures"
output: html_document
---
This script runs the testing cost effectiveness transmission function and outputs figure for the main text of the manuscript. 
The difference between these figures/analysis and what is used in the app is that this incorporates uncertainty-- i.e. for a testing policy to be optimal we need to be 95% sure based on the parameter ranges given, that the symptomatic cases over the past 7 days won't 
exceed the threshold set.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(ggplot2)
library(deSolve)
library(scales)
library(dplyr)
library(EpiEstim)
library(tidyr)
library(reshape2)
library(cowplot)
library(knitr)
library(forcats)
library(bigsnpr)
library(EnvStats)
library(tidyverse)
library(ggpubr)
library(zoo)
library(lubridate)
source("testing_cost_effectiveness_fxns.R")
theme_set(theme_cowplot())
ggplot + background_grid(major = "xy", minor = "xy")
PAR_TABLE_PATH<-'par_table.csv'
COST_TABLE_PATH<-'cost_table.csv'
PAR_BOUNDS_PATH<-'par_bounds.csv'
```

```{r}
case_detection_rate = 1/4.2 # CDC study

# vaccine and immunity parameters 
e_v = 0.8 # Singapore study showing vaccinated infected almost as transmissibile (same viral laod) as unvaccinated infected
sigma_v = 0.47 # https://www.cdc.gov/mmwr/volumes/70/wr/mm7034e3.htm corresponding to 53% effective against infection
sym_red = 0.36  # https://www.gov.il/en/departments/news/06072021-04 corresponding to 64% effective against symptomatic infection
psym_v = sym_red/sigma_v


# test parameters
Sp = 0.995 # test specificity
Se = 0.9 # test sensitivity
w_v = 0.75 # proportion of vaccinated population willing to test
w_u = 0.75 # proportion of unvaccinated population willing to test
f_v = 0 # frequency of testing in vaccinated individuals
f_u =0 # frequency of testing in unvaccinated individuals
is = 0.925 # probability of isolating given a positive test (survey somewhere)
is_sym = 0.25 # probability of isolating/seeking a test given symptoms
k = 1/2 # rate of confirmation testing
r_r = 1/7 # rate of leaving quarantine asymptomatic or symptomatic quarantine states

# scenario parameters
N<- 50000
duration_school_year = 113
tdays<-seq(from = 0, to = duration_school_year, by = 1)
dates<-seq(from = as.Date("2021-08-25"), by = "day", length.out = duration_school_year+1)

# epidemiological parameters
R0 = 5
t_exposed = 3
t_pre_sym = 2.3
t_inf = 7
t_sym_state = t_inf-t_pre_sym
t_quarantine = 7
t_iso = 2 # time to isolate if symptomatic
psym = 0.6 # symptomatic rate-- Davies et al, need to adjust by age group
community_cases_per_100k = 29 # using NYT case counts for Travis county as of 9/22/2021
#intros_per_week =7*0.1*(community_cases_per_100k/100000)/case_detection_rate*N # assumes 10% interaction with community, 1 in 4 case detection rate 
intros_per_week = 10
avg_time_asym = psym*t_pre_sym + (1-psym)*t_inf
avg_time_asym_v= psym_v*t_pre_sym + (1-psym_v)*t_inf
# sanity checks (these don't go into par table)
delta_au = 1/avg_time_asym
delta_av = 1/avg_time_asym_v
delta_s = 1/t_sym_state
delta_q = 1/t_quarantine
beta_a = R0*1/t_inf #transmission rate of asymptomatic individuals
beta_s = R0*1/t_inf # transmission rate of symptomatic individuals 

gamma = 1/3 # rate of transition from exposed to infectious
init_prev = 420/100000 # initial disease prevalence on campus using UT report
init_rec = 0.32
init_vacc = 0.57 # using UT report 
odds_inf_not_vac = 1
init_ru = init_rec- init_rec*init_vacc
init_rv = init_rec*init_vacc
init_sv = (1-init_rec)*init_vacc 



# cost parameters
PCR_price = 100 # modified this since most PCR costs 50-100
RT_price = 6
online_price = 100000 # based on conversations with UT administrators 
pct_pos_isofac = 0.2# percent of students that would use isofac (7400 living on campus,
#plus small percent living off campus in shared rooms)
# (this could be higher at other universities, so possibly we might want to include this in the app )
isofac_price = 300 #  $ dollars per student per day
contact_tracing_price = 50 # cost of labor to reach out to each cases contacts (is this still accurate given high numbers of contacts?)
sequencing_price = 100 # assumes all PCR positives get sequences 
DLL_price = 500*15/135#500 per credit * 18 credits per semester/ 135 days per semester
risk_tolerance = '1.5x CDC red' 


# Uncertainty
nsamps<-100
R0vals<-c(4.5, 5.5)
init_rec_vals<-c(0.27, 0.37) # CDC seroprevalence?
psym_vals<-c(0.55, 0.65)
sigma_v_vals<-c(0.37, 0.5) # from 63% effective to 50% effective at preventing infection? israeli to CDC estimate 
sym_red_vals<-c(0.27, 0.37) # from 73% effective to 64% effective at preventing symptomatic infection
is_vals<-c(0.925, 0.925) # remove uncertainty here for now
is_sym_vals<-c(0.24, 0.28) # ranges from 1 in 4.2 to 1 in 3.6 of symptomatic detection/seeking 
intro_vals<-c(intros_per_week*0.75, intros_per_week*1.25) # assume 25% increase or decrease from current assumption 
init_vacc_vals<-c(0.46, 0.64)
init_prev_vals<-c(init_prev*0.75, init_prev*1.25) # assume 25% increase or decrease from current assumption





cost_table<-data.frame(PCR_price, RT_price, online_price, DLL_price, pct_pos_isofac,
                       isofac_price, contact_tracing_price, sequencing_price) 

par_table<-data.frame(N, init_prev, init_rec, init_vacc, odds_inf_not_vac, duration_school_year, R0,
                      t_pre_sym,
                      t_inf, t_sym_state, t_quarantine,t_iso,  psym, gamma,psym, e_v, sigma_v,
                      sym_red,intros_per_week,
                      Sp, Se, w_v, w_u, f_v,f_u, is,is_sym, k)
par_bounds<-data.frame(R0vals,init_rec_vals, psym_vals, sigma_v_vals, sym_red_vals, is_sym_vals, is_vals, intro_vals, init_prev_vals, init_vacc_vals)
write.csv(cost_table, 'cost_table.csv',row.names = FALSE)
write.csv(par_table,'par_table.csv', row.names = FALSE)
write.csv(par_bounds, 'par_bounds.csv', row.names = FALSE)
```
Test uncertainty function and simulation output (show individual spaghettis for two different scenarios)
```{r}
par_table$f_u<-2/7
par_table$f_v<-2/7
par_table$init_vacc<-0.7
nsamps<-10
out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance, nsamps, par_bounds)
aggr_df_t<-out_list_uq[[4]]
aggr_df<-out_list_uq[[3]]
df_t_sims<-out_list_uq[[2]]

out_df<-solve_transmission_eqns(par_table)

par_table$f_u<-0
par_table$f_v<-0
out_nt_df<-solve_transmission_eqns(par_table)
out_list_uq_nt<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance, nsamps, par_bounds)
aggr_df_t_nt<-out_list_uq_nt[[4]]
df_t_sims_nt<-out_list_uq_nt[[2]]

Iplot<-ggplot() + geom_line(data = df_t_sims , aes(x = dates, y = I, group = sample), color = "blue", alpha = 0.1) + geom_line(data = aggr_df_t , aes(x = dates, y = I_med), color = "blue")  + geom_line(data = df_t_sims_nt, aes(x = dates, y = I, group = sample), color = "red", alpha = 0.1) + geom_line(data = aggr_df_t_nt, aes (x = dates, y = I_med), color = "red") +  scale_x_date(labels = date_format("%b"), breaks = date_breaks("month")) + xlab('Date') + ylab ('Infections')
Iplot

Isymdetplot<-ggplot() + geom_line(data = df_t_sims , aes(x = dates, y = Isymdet, group = sample), color = "blue", alpha = 0.1) + 
  geom_line(data = aggr_df_t , aes(x = dates, y = Isymdet_med), color = "blue")  +
  geom_line(data = df_t_sims_nt, aes(x = dates, y = Isymdet, group = sample), color = "black", alpha = 0.1) + 
  geom_line(data = aggr_df_t_nt, aes (x = dates, y = Isymdet_med), color = "black") +
  geom_hline(yintercept = N*100/100000, linetype = "dashed", color = "red") +
  geom_hline(yintercept = N*150/100000, linetype = "dashed", color = "purple") +  
  scale_x_date(labels = date_format("%b"), breaks = date_breaks("month")) +
  xlab('Date') + 
  ylab ('Symptomatic detected infections') +
  coord_cartesian(ylim = c(0,300))
Isymdetplot
```
Vary vaccine coverage, and within each vaccine coverage, simulate different testing frequencies for unvaccinated population. For each vaccine coverage and potentially disease prevalence, find the minimal amount of testing that prevents the university from having to move classes online.
```{r}
# Best estimate of the current epidemiological scenario
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
nsamps<-100# for now set to 10 for troubleshooting( make this 100 for final results)
risk_tolerance = '2x CDC red'
vacc_coverage<-seq(from = 0.5, to = 0.9, by = 0.1)
test_freqs<-c(0, 1/30, 1/14, 1/7, 2/7, 3/7, 1)
test_policies<-c('only symptomatic', 'monthly', '2 times per month', 'weekly', '2 times per week', '3 times per week', 'daily')
vacc_policy<-c( '50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated', '90% vaccinated')

N<-par_table$N

tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-25"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(vacc_coverage)){
    pct_vacc<-vacc_coverage[j]
    par_table$init_vacc<-vacc_coverage[j]
    vacc_cov<-rep(vacc_coverage[j], par_table$duration_school_year+1)
    vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
    vacc_rate<-vacc_policy[j]
    for (k in 1:length(test_freqs)){
      testing_freq<-test_freqs[k]
      testing_policy<-test_policies[k]
      par_table$f_u<-test_freqs[k]
      par_table$f_v<-test_freqs[k]
      population_tested<-"all students"
      test_freq<-rep(test_freqs[k], par_table$duration_school_year+1)
      test_policy<-rep(test_policies[k], par_table$duration_school_year+1)
      testing_policy<-test_policies[k]
      #out_df<-solve_transmission_eqns(par_table)
      #summary_df<-testing_model(par_table, cost_table, risk_tolerance)
      # Get the outputs from each sample and the aggregate outputs over time and in summary
      out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds)
      df_sim<-out_list_uq[[1]] # contains final results for all nsims
      df_t_sim<-out_list_uq[[2]] # contains time course of results for all nsims
      aggr_df<-out_list_uq[[3]] # contains lb, ub, median of final results 
      aggr_df<-cbind(aggr_df,testing_policy,population_tested, vacc_rate)
      aggr_df_t<-out_list_uq[[4]] # contains time course of lb, ub, median of results
      aggr_df_t<-cbind(aggr_df_t, test_policy, vacc_policies)
    
      
      if(k ==1 & j==1){
        df<-df_sim
        df_t<-df_t_sim
        df_uq<-aggr_df
        df_t_uq<-aggr_df_t
    
      }
      else{
        df<-rbind(df, df_sim)
        df_t<-rbind(df_t, df_t_sim)
        df_uq<-rbind(df_uq, aggr_df)
        df_t_uq<-rbind(df_t_uq, aggr_df_t)
      }
      
    }
  }

```
For each vaccine coverage, find the minimum testing needed at each risk tolerance level
```{r}
threshold_prob = 0.05
df_small<-df_uq%>%select(pct_vacc_med, testing_freq_med, days_of_online_med, days_of_online_ub, cross_2xred_prob)
df_min<-get_min_testing_per_vacc(df_uq,threshold_prob, vacc_coverage)
df_min$testing_policy<-factor(df_min$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic", "monthly", "2 times per month", "weekly", "2 times per week", "3 times per week", "daily")))

write.csv(df_uq,'../out/summary_results.csv',row.names = FALSE )
write.csv(df_t_uq, '../out/results_t.csv', row.names = FALSE)
write.csv(df_min, '../out/min_testing.csv', row.names = FALSE)
```
Load in the data frames if don't want to rerun, make smaller dataframe for the main tables

```{r}
close_thres = case_when(
         risk_tolerance == "CDC red" ~ 100/100000,
         risk_tolerance == "1.5x CDC red" ~ 150/100000,
         risk_tolerance == "2x CDC red" ~200/100000)
df_uq<-read.csv('../out/summary_results.csv')
df_t_uq<-read.csv('../out/results_t.csv')
df_min<-read.csv('../out/min_testing.csv')
df_print<-df_uq%>%select(pct_vacc_med,testing_policy, n_inf_med, n_inf_lb, n_inf_ub, max_symdet_med, max_symdet_lb, max_symdet_ub, cost_to_UT_med, cost_testing_per_student_med)

df_t_uq$test_policy<-factor(df_t_uq$test_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic", "monthly", "2 times per month", "weekly",
                         "2 times per week", "3 times per week", "daily")))

path = "../out/sym_det_t_all.png"
# First plot testing needed
thres_sym_det<-ggplot(df_t_uq) + 
  geom_line(aes(x = time, y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) +
  geom_ribbon(aes(x = time, ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+ 
  facet_grid(~vacc_policies)+
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed") + 
  labs(color = "Test frequency") + 
  xlab('Time (days)') + 
  ylab('Symptomatic Detected Cases')+ 
  scale_color_brewer(palette = "Set2", direction = -1) +scale_fill_brewer(palette = "Set2", direction = -1) + coord_cartesian(ylim = c(0,6*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + theme(legend.position = "bottom", legend.text= element_text(size = 12)) + guides(fill = FALSE) 
thres_sym_det
ggsave(filename = path, device = "png", dpi = 700)


path = "../out/sym_det_t_sel.png"
# First plot testing needed
df_t_uq_sel<-df_t_uq%>%filter(pct_vacc_med ==0.6 | pct_vacc_med == 0.9)
thres_sym_det_sel<-ggplot(df_t_uq_sel) + 
  geom_line(aes(x = time, y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) + 
  geom_ribbon(aes(x = time, ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+ 
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed")+ 
  facet_grid(~vacc_policies)+
  labs(color = "Test frequency") + 
  xlab('Time (days)') + 
  theme_bw()+
  ylab('Symptomatic Detected Cases')  + 
  scale_color_brewer(palette = "Set2", direction = -1) +
  scale_fill_brewer(palette = "Set2", direction = -1) + 
  coord_cartesian(ylim = c(0,6*N*close_thres )) + # was 2*
  theme(axis.text.x = element_text(angle=45, hjust = 1)) +
  theme(aspect.ratio = 1, legend.position = "right", legend.text= element_text(size = 11)) +  
  guides(fill = FALSE) 
thres_sym_det_sel
ggsave(filename = path, device = "png", dpi = 700)

thres_sym_det_sel<-ggplot(df_t_uq_sel) + 
  geom_line(aes(x = ymd(dates), y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) + 
  geom_ribbon(aes(x = ymd(dates), ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+ 
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed")+ 
  facet_grid(~vacc_policies)+
  labs(color = "Test frequency") + 
  xlab('Date') + 
  ylab('Symptomatic Detected Cases')  + 
  scale_color_brewer(palette = "Set2", direction = -1) +
  scale_fill_brewer(palette = "Set2", direction = -1) + 
  scale_x_date(date_labels = "%b")+
  coord_cartesian(ylim = c(0,6*N*close_thres )) + # was 2*
  theme(axis.text.x = element_text(angle=45, hjust = 1)) +
  theme(aspect.ratio = 1, legend.position = "right", legend.text= element_text(size = 11)) +  
  guides(fill = FALSE) 
thres_sym_det_sel
ggsave(filename = path, device = "png", dpi = 700)


```

Make cost breakdown figures for all levels of testing and vaccination
```{r}
df_long<-df_uq%>%
  dplyr::select(pct_vacc_med, vacc_rate, testing_freq_med, testing_policy,
                              pct_inf_med, cost_PCR_med,
                              cost_RT_med, cost_isofac_med, cost_sequencing_med, 
                              cost_contact_tracing_med, cost_of_online_med, cost_testing_per_student_med)%>%
  pivot_longer(cols = starts_with("cost_"),names_to = "Source",names_prefix = "cost_", values_to = "cost" )%>%mutate(test_strategy = 'yes')
df_long$testing_policy<-factor(df_long$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic","monthly", 
                                       "2 times per month", "weekly", "2 times per week", "3 times per week",
                                       "daily")))
df_uq$testing_policy<-factor(df_uq$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic","monthly", 
                                       "2 times per month", "weekly", "2 times per week", "3 times per week",
                                       "daily")))


df_long$Source<-factor(df_long$Source, ordered = TRUE,
                         stringr::str_wrap(c("of_online_med", "contact_tracing_med",
                                             "isofac_med", "PCR_med","sequencing_med", "RT_med")))
path = "../out/cost_breakdown.png"
bar_costs_comb<-ggplot(df_long, aes (x = testing_policy, y = cost/1e6, fill = factor(Source))) + 
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~vacc_rate, ncol = 6) +  
  xlab('Test Frequency') + 
  ylab('Cost to university (millions)') +
  scale_fill_manual(" Source of Cost",values = c('gray', 'pink', 'coral2',  'orange', 'yellow', 'blue4'),
                         breaks = c('of_online_med', 'contact_tracing_med', 'isofac_med', 
                                                'PCR_med', "sequencing_med", "RT_med"),
                         labels =c('online', 'contact tracing', 'isolation', 
                                   'confirmatory PCR', 'sequencing', 'proactive (rapid) tests')) + 
  theme(legend.position = "right", axis.text.y = element_text(size = 10), axis.title = element_text(size = 12)) + theme(axis.text.x = element_text(angle=35, hjust = 1, size = 10), aspect.ratio =1.3) 
bar_costs_comb
ggsave(filename = path, device = "png", dpi = 700)
path = "../out/cost_breakdown_sel.png"
df_long_sel<-df_long%>%filter(pct_vacc_med == 0.6 | pct_vacc_med == 0.9)
bar_costs_comb_sel<-ggplot(df_long_sel, aes (x = testing_policy, y = cost/1e6, fill = factor(Source))) + 
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~vacc_rate, ncol = 6) +  
  xlab('Test Frequency') + 
  ylab('Cost to university (millions)') +
  scale_fill_manual(" Source of Cost",values = c('gray', 'pink', 'coral2',  'orange', 'yellow', 'blue4'),
                         breaks = c('of_online_med', 'contact_tracing_med', 'isofac_med', 
                                                'PCR_med', "sequencing_med", "RT_med"),
                         labels =c('online', 'contact tracing', 'isolation', 
                                   'confirmatory PCR', 'sequencing', 'proactive (rapid) tests')) + 
  theme(legend.position = "none", axis.text.y = element_text(size = 10), axis.title = element_text(size = 12)) + theme(axis.text.x = element_text(angle=40, hjust = 1, size = 10)) 
bar_costs_comb_sel
ggsave(filename = path, device = "png", dpi = 700)



path = "../out/inf_by_vax_rate.png"
bar_inf<-ggplot(df_uq, aes(x = testing_policy, y = n_inf_med/1000)) +
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~vacc_rate, ncol = 6) + 
  geom_errorbar(aes(ymin = n_inf_lb/1000, ymax= n_inf_ub/1000), width = 0.1, position = position_dodge(0.04)) +
  xlab('Test frequency') + ylab('Infections (thousands)')  + 
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), axis.title = element_text(size = 12), legend.position = "none", aspect.ratio =1.3)
bar_inf
ggsave(filename = path, device = "png", dpi = 700)

path = "../out/inf_by_vax_rate_sel.png"
df_uq_sel <-df_uq%>%filter(pct_vacc_med == 0.6 | pct_vacc_med == 0.9)
bar_inf_sel<-ggplot(df_uq_sel, aes(x = testing_policy, y = n_inf_med/1000)) +
  geom_bar(stat = "identity", position = "stack") + 
  facet_wrap(~vacc_rate, ncol = 6) + 
  geom_errorbar(aes(ymin = n_inf_lb/1000, ymax= n_inf_ub/1000), width = 0.1, position = position_dodge(0.04)) +
  xlab('Test frequency') + ylab('Infections (thousands)')  + 
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), axis.title = element_text(size = 12), legend.position = "none", aspect.ratio = 1.0)
bar_inf_sel
ggsave(filename = path, device = "png", dpi = 700)
```
Plot the minimum amount of testing needed at each vaccination level and the chosen risk tolerance
```{r}
df_min_print<-df_min%>%filter(thres == "2x CDC high" )%>%select(pct_vacc_med, testing_policy,population_tested, 
                                                         testing_freq_med, n_tests_per_week_med,
                                                      n_inf_med, n_inf_lb, n_inf_ub, n_inf_nt_med, cost_to_UT_med,
                                                      cost_to_UT_lb, cost_to_UT_ub, cost_per_inf_averted_med, 
                                                      cost_per_inf_averted_lb, cost_per_inf_averted_ub,
                                                      cost_per_DO_averted_med, cost_testing_per_student_med, cost_per_DO_averted_lb, cost_per_DO_averted_ub)

path = '../out/test_freq_req.png'
bar_test_freq<-ggplot(df_min_print, aes(x = 100*pct_vacc_med, y = 7*testing_freq_med)) + geom_bar(stat = "identity", position = position_dodge())  + xlab('Percent vaccinated') + ylab('Recommended frequency (tests per week)') + guides(fill = FALSE)+theme(aspect.ratio = 1, axis.title.y = element_text(size =14))
bar_test_freq
ggsave(filename = path, device = "png", dpi = 700)
path = '../out/tot_tests_req.png'
bar_tot_tests<-ggplot(df_min_print, aes(x = 100*pct_vacc_med, y = n_tests_per_week_med)) + geom_bar(stat = "identity", position = position_dodge()) + xlab('Percent vaccinated') + ylab('Total tests per week')+guides(fill = FALSE) + theme(aspect.ratio = 1)
bar_tot_tests
ggsave(filename = path, device = "png", dpi = 700)
```
Sensitivity analysis on vaccine efficacy against infection/symptoms 
```{r}
nsamps<-10
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_bounds<-read.csv(PAR_BOUNDS_PATH)
e_v_vec<-c(1, 0.9, 0.8, 0.7, 0.6, 0.5)

pct_vacc_vec<-seq(from = 0.5, to = 0.9, by = 0.1)
vacc_policy<-c('50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated', '90% vaccinated')
vacc_eff_against_transmission_vec<-c('same transmissibility', 'reduces by 10%', 'reduces by 20%', 'reduces by 30%', 'reduces by 40%', 'reduces by 50%')
population_tested= "all students"
par_table$f_v<- 1/7
par_table$f_u<- 1/7 # weekly testing for all 

N<-par_table$N
tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-20"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(pct_vacc_vec)){
    par_table$init_vacc<-pct_vacc_vec[j]
    vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
    for (k in 1:length(e_v_vec)){
      par_table$e_v<- e_v_vec[k]
      vacc_eff_against_transmission<-rep(vacc_eff_against_transmission_vec[k],  par_table$duration_school_year +1)
      out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds)
      df_sim<-out_list_uq[[1]]
      df_t_sim<-out_list_uq[[2]]
      aggr_df<-out_list_uq[[3]]
      aggr_df_t<-out_list_uq[[4]]
      aggr_df_t<-cbind(aggr_df_t, vacc_policies, vacc_eff_against_transmission)
      if(k ==1 & j==1){
        df<-df_sim
        df_t<-df_t_sim
        df_uq<-aggr_df
        df_t_uq<-aggr_df_t
    
      }
      else{
        df<-rbind(df, df_sim)
        df_t<-rbind(df_t, df_t_sim)
        df_uq<-rbind(df_uq, aggr_df)
        df_t_uq<-rbind(df_t_uq, aggr_df_t)
      }
      
    }
}
df_t_uq$vacc_eff_against_transmission<-factor(df_t_uq$vacc_eff_against_transmission, ordered = TRUE,
                         stringr::str_wrap(c("same transmissibility", "reduces by 10%", "reduces by 20%", "reduces by 30%", 
                                             "reduces by 40%","reduces by 50%" )))
N = 50000
path = "../out/sens_analysis_vacc_eff_transmission.png"
# First plot testing needed
sensitivity_to_vacc_eff_transmission<-ggplot(df_t_uq) + 
  geom_line(aes(x = time, y = Isymdet_med, group = factor(vacc_eff_against_transmission), color = factor(vacc_eff_against_transmission))) + 
  geom_ribbon(aes(x = time, ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(vacc_eff_against_transmission), fill = factor(vacc_eff_against_transmission)), alpha = 0.1)+ 
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed") +
  facet_grid(~vacc_policies) + labs(color = "VE against transmission") + xlab('Time (days)') + ylab('Symptomatic Detected Cases')  + 
  scale_color_brewer(palette = "RdYlBu", direction = -1) +
  scale_fill_brewer(palette = "RdYlBu", direction = -1) + 
  coord_cartesian(ylim = c(0,6*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + 
  theme(legend.position = "bottom", legend.text= element_text(size = 12)) + guides(fill = FALSE) + 
  labs(color = "VE against transmission")
sensitivity_to_vacc_eff_transmission
ggsave(filename = path, device = "png", dpi = 700)

```
Sensitivity analysis on vaccine efficacy against transmission
```{r}
nsamps<-100
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_bounds<-read.csv(PAR_BOUNDS_PATH)
VE_against_inf_vec<-seq(from = 0.4, to = 0.7, by = 0.1)
VE_against_symptoms_vec<-VE_against_inf_vec+ 0.15 # generally seems to be the pattern, but idk
pct_vacc_vec<-seq(from = 0.5, to = 0.9, by = 0.1)
par_table$f_u<-0
vacc_policy<-c('50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated', '90% vaccinated')
vacc_eff_vec<-c('40% against infection, 55% symptoms', '50% against infection, 65% symptoms', '60% against infection, 75% symptoms',
            '70% against infection, 85% symptoms')
population_tested= "all students"
par_table$f_v<- 1/7
par_table$f_u<- 1/7 # weekly testing for all 

N<-par_table$N
tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-20"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(pct_vacc_vec)){
    par_table$init_vacc<-pct_vacc_vec[j]
    vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
    for (k in 1:length(VE_against_inf_vec)){
      par_table$sigma_v<- 1-VE_against_inf_vec[k]
      par_table$sym_red<- 1- VE_against_symptoms_vec[k]
      par_bounds$sigma_v_vals<-c(par_table$sigma_v*(0.37/0.47), par_table$sigma_v*0.5/0.47) # from 63% effective to 50% effective at preventing infection? israeli to CDC estimate 
      par_bounds$sym_red_vals<-par_bounds$sigma_v_vals - 0.15
      VE_against_inf<-rep(VE_against_inf_vec[k],  par_table$duration_school_year +1)
      VE_against_symptoms<-rep(VE_against_symptoms_vec[k],  par_table$duration_school_year +1)
      vacc_eff<-rep(vacc_eff_vec[k], par_table$duration_school_year+1)
      out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds)
      df_sim<-out_list_uq[[1]]
      df_t_sim<-out_list_uq[[2]]
      aggr_df<-out_list_uq[[3]]
      aggr_df_t<-out_list_uq[[4]]
      aggr_df_t<-cbind(aggr_df_t, vacc_policies, vacc_eff, VE_against_inf, VE_against_symptoms)
      if(k ==1 & j==1){
        df<-df_sim
        df_t<-df_t_sim
        df_uq<-aggr_df
        df_t_uq<-aggr_df_t
    
      }
      else{
        df<-rbind(df, df_sim)
        df_t<-rbind(df_t, df_t_sim)
        df_uq<-rbind(df_uq, aggr_df)
        df_t_uq<-rbind(df_t_uq, aggr_df_t)
      }
      
    }
}

N = 50000
path = "../out/sens_analysis_vacc_eff.png"
# First plot testing needed
sensitivity_to_vacc_eff<-ggplot(df_t_uq) + 
  geom_line(aes(x = time, y = Isymdet_med, group = factor(vacc_eff), color = factor(vacc_eff))) + 
  geom_ribbon(aes(x = time, ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(vacc_eff), fill = factor(vacc_eff)), alpha = 0.1)+ 
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed") +
  facet_grid(~vacc_policies) + labs(color = "VE against infection") + xlab('Time (days)') + ylab('Symptomatic Detected Cases')  + 
  scale_color_brewer(palette = "BrBG", direction = -1) +
  scale_fill_brewer(palette = "BrBG", direction = -1) + 
  coord_cartesian(ylim = c(0,6*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + 
  theme(legend.position = "bottom", legend.text= element_text(size = 12)) + guides(fill = FALSE) + 
  labs(color = "VE against infection")
sensitivity_to_vacc_eff
ggsave(filename = path, device = "png", dpi = 700)

```


Repeat the same analysis, but also do 2x the testing in unvax, and only testing in unvax
```{r}
# Best estimate of the current epidemiological scenario
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_bounds<-read.csv(PAR_BOUNDS_PATH)
nsamps<-100# for now set to 10 for troubleshooting( make this 100 for final results)
risk_tolerance = '2x CDC red'
vacc_coverage<-seq(from = 0.5, to = 0.9, by = 0.1)
test_freqs<-c(0, 1/30, 1/14, 1/7, 2/7, 3/7, 1)
test_policies<-c('only symptomatic', 'monthly', '2 times per month', 'weekly', '2 times per week', '3 times per week', 'daily')
vacc_policy<-c( '50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated', '90% vaccinated')
population_tested_vec<-c('all students equally', 'half the rate in vax', 'unvaccinated only')


N<-par_table$N

tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-25"), by = "day", length.out = par_table$duration_school_year+1)
for (i in 1:length(population_tested_vec)){
  population_tested<-population_tested_vec[i]
  pop_tested<-rep(population_tested_vec[i],par_table$duration_school_year+1)
  for(j in 1:length(vacc_coverage)){
      pct_vacc<-vacc_coverage[j]
      par_table$init_vacc<-vacc_coverage[j]
      vacc_cov<-rep(vacc_coverage[j], par_table$duration_school_year+1)
      vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
      vacc_rate<-vacc_policy[j]
      for (k in 1:length(test_freqs)){
        testing_freq<-test_freqs[k]
        testing_policy<-test_policies[k]
        par_table$f_u<-test_freqs[k]
        # Set the testing rate in vaccinated based on 
        freq_vacc = case_when(
         population_tested == "all students equally" ~ test_freqs[k],
         population_tested == "half the rate in vax" ~ 0.5*test_freqs[k],
         population_tested == "unvaccinated only" ~0)
        par_table$f_v<-freq_vacc
        test_freq<-rep(test_freqs[k], par_table$duration_school_year+1)
        test_policy<-rep(test_policies[k], par_table$duration_school_year+1)
        testing_policy<-test_policies[k]
      # Get the outputs from each sample and the aggregate outputs over time and in summary
        out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds)
        df_sim<-out_list_uq[[1]] # contains final results for all nsims
        df_t_sim<-out_list_uq[[2]] # contains time course of results for all nsims
        aggr_df<-out_list_uq[[3]] # contains lb, ub, median of final results 
        aggr_df<-cbind(aggr_df,testing_policy,population_tested, vacc_rate)
        aggr_df_t<-out_list_uq[[4]] # contains time course of lb, ub, median of results
        aggr_df_t<-cbind(aggr_df_t, test_policy, pop_tested, vacc_policies)
    
      
        if(k ==1 & j==1 & i==1){
          df<-df_sim
          df_t<-df_t_sim
          df_uq<-aggr_df
          df_t_uq<-aggr_df_t
    
        }
        else{
          df<-rbind(df, df_sim)
          df_t<-rbind(df_t, df_t_sim)
          df_uq<-rbind(df_uq, aggr_df)
          df_t_uq<-rbind(df_t_uq, aggr_df_t)
        }
      }
    }
  }

```
For each vaccine coverage, find the minimum testing needed at each risk tolerance level
```{r}
threshold_prob = 0.05
df_small<-df_uq%>%select(pct_vacc_med, testing_freq_med, population_tested, days_of_online_med, days_of_online_ub, cross_2xred_prob)
for (i in 1:length(population_tested_vec)){
  df_test<-df_uq%>%filter(population_tested == population_tested_vec[i])
df_mini<-get_min_testing_per_vacc(df_test,threshold_prob, vacc_coverage)
  if (i==1){
    df_min<-df_mini
  }
  else{
    df_min<-rbind(df_min, df_mini)
  }
}

df_min$testing_policy<-factor(df_min$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic", "monthly", "2 times per month", "weekly", "2 times per week", "3 times per week", "daily")))

write.csv(df_uq,'../out/summary_results3.csv',row.names = FALSE )
write.csv(df_t_uq, '../out/results_t3.csv', row.names = FALSE)
write.csv(df_min, '../out/min_testing3.csv', row.names = FALSE)
```
Plot figure 1 with 3 rows for the three test policy options, then figure 2 with all policy options
```{r}
close_thres = case_when(
         risk_tolerance == "CDC red" ~ 100/100000,
         risk_tolerance == "1.5x CDC red" ~ 150/100000,
         risk_tolerance == "2x CDC red" ~200/100000)
df_uq<-read.csv('../out/summary_results3.csv')
df_t_uq<-read.csv('../out/results_t3.csv')
df_min<-read.csv('../out/min_testing3.csv')
df_print<-df_uq%>%select(pct_vacc_med,testing_policy, population_tested, n_inf_med, n_inf_lb, n_inf_ub, max_symdet_med, max_symdet_lb, max_symdet_ub, cost_to_UT_med, n_inf_nt_med)

df_t_uq$test_policy<-factor(df_t_uq$test_policy, ordered = TRUE,
                         stringr::str_wrap(c("only symptomatic", "monthly", "2 times per month", "weekly",
                         "2 times per week", "3 times per week", "daily")))

path = "../out/sym_det_t_all_policies.png"
# First plot testing needed
thres_sym_det<-ggplot(df_t_uq) + 
  geom_line(aes(x = time, y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) +
  geom_ribbon(aes(x = time, ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+
  facet_grid(pop_tested~vacc_policies)+
  geom_hline(yintercept = N*close_thres, color = "red", linetype = "dashed") + 
  labs(color = "Test frequency") + 
  xlab('Time (days)') + 
  ylab('Symptomatic Detected Cases')+ 
  scale_color_brewer(palette = "Set2", direction = -1) +scale_fill_brewer(palette = "Set2", direction = -1) + coord_cartesian(ylim = c(0,6*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1), 
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 8),
        legend.position = "none",
        legend.text= element_text(size = 12)) + guides(fill = FALSE) 
thres_sym_det
ggsave(filename = path, device = "png", dpi = 700)

df_min_print<-df_min%>%filter(thres == "2x CDC high" )%>%select(pct_vacc_med, testing_policy, population_tested, 
                                                         testing_freq_med, cost_testing_per_student_med, n_tests_per_week_med,
                                                      n_inf_med, n_inf_lb, n_inf_ub, n_inf_nt_med, cost_to_UT_med,
                                                      cost_to_UT_lb, cost_to_UT_ub, cost_per_inf_averted_med, 
                                                      cost_per_inf_averted_lb, cost_per_inf_averted_ub,
                                                      cost_per_DO_averted_med, cost_per_DO_averted_lb, cost_per_DO_averted_ub)

path = '../out/test_freq_req.png'
bar_test_freq<-ggplot(df_min_print, aes(x = 100*pct_vacc_med, y = 7*testing_freq_med, fill = population_tested)) + 
  geom_bar(stat = "identity", position = position_dodge())  + 
  scale_fill_manual("Population tested",values = c('blue3', 'purple3', 'red3'),
                         breaks = c('all students equally', 'half the rate in vax', 'unvaccinated only'),
                         labels =c('all students', 'half the rate in vaccinated', 'unvaccinated only')) +
  xlab('Percent vaccinated') + ylab('Recommended frequency (tests per week)') + 
  theme(aspect.ratio = 1, axis.title.y = element_text(size =14))
bar_test_freq
ggsave(filename = path, device = "png", dpi = 700)
path = '../out/tot_tests_req.png'
bar_tot_tests<-ggplot(df_min_print, aes(x = 100*pct_vacc_med, y = n_tests_per_week_med, fill = population_tested)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_fill_manual("Population tested",values = c('blue3', 'purple3', 'red3'),
                         breaks = c('all students equally', 'half the rate in vax', 'unvaccinated only'),
                         labels =c('all students', 'half the rate in vaccinated', 'unvaccinated only'))+
  xlab('Percent vaccinated') + ylab('Total tests per week') + theme(aspect.ratio = 1)
bar_tot_tests
ggsave(filename = path, device = "png", dpi = 700)

path = '../out/tot_costs.png'
bar_tot_costs<-ggplot(df_min_print, aes(x = 100*pct_vacc_med, y = cost_to_UT_med/1e6, fill = population_tested)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  xlab('Percent vaccinated') + ylab('Cost to university (millions)')+
 theme(aspect.ratio = 1)
bar_tot_costs
ggsave(filename = path, device = "png", dpi = 700)
```